Report

### 2021-10-21 Rmd/report.Rmd

---
title: "Cognate Priming: Report"
output:
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dpi = 150,
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		knitr.duplicate.label = "allow",
		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(gt)
library(patchwork)
library(wesanderson)
library(shiny)
library(tidytext)
library(brms)
library(tidyverse)
library(here)

@@

theme_set(theme_github()) # in utils.R
```

@@

@@

```{r child="report_06_vocabulary_stringent.Rmd"}
```

@@

```{r child="report_06_vocabulary_relaxed.Rmd"}
```

>>>>

---
title: "Report"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
		ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

# load packages
library(targets)
library(papaja)
library(knitr)
library(tidyverse)
library(lubridate)
library(scales)
library(DiagrammeR)
library(janitor)
library(lme4)
library(broom.mixed)
library(gt)
library(patchwork)
library(htmltools)
library(wesanderson)
library(shiny)
library(tidytext)
library(here)

@@

theme_set(theme_custom()) # in utils.R
```

@@

### Counterbalancing {.tabset}

#### Stringent criteria {.tabset}

```{r child="report_05_attrition_counter_stringent.Rmd"}
```

#### Relaxed criteria {.tabset}

```{r child="report_05_attrition_counter_relaxed.Rmd"}
```

#### {-}

## 21 months-old monolinguals {.tabset}

```{r child="report_06_21-mon_stringent.Rmd"}
```

```{r child="report_06_21-mon_relaxed.Rmd"}
```

## 21 and 25 months-old monolinguals {.tabset}

```{r child="report_07_2125-mon_stringent.Rmd"}
```

```{r child="report_07_2125-mon_relaxed.Rmd"}
```

## 21, 25, and 30 months-old monolinguals {.tabset}

```{r child="report_08_mon_stringent.Rmd"}
```

### Relax

```{r child="report_08_mon_relaxed.Rmd"}
```

@@

```{r child="report_09_vocabulary_stringent.Rmd"}
```

@@

```{r child="report_09_vocabulary_relaxed.Rmd"}
```

### 2021-10-21 Rmd/report_06_21-mon_relaxed.Rmd

```{r define_model_21_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_21_mon <- model_fits_relaxed$fit_21_mon
fit_21_mon_location <- model_fits_relaxed$fit_21_mon_location
fit_21_mon_vocab_split<- model_fits_relaxed$fit_21_mon_vocab_split
fit_21_mon_vocab_balanced <- model_fits_relaxed$fit_21_mon_vocab_balanced
```

@@

>>>>

```{r define_model_21_mon_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_21_mon <- model_fits_relaxed$fit_21_mon
fit_21_mon_location <- model_fits_relaxed$fit_21_mon_location
fit_21_mon_frequency <- model_fits_relaxed$fit_21_mon_frequency
fit_21_mon_vocab_split<- model_fits_relaxed$fit_21_mon_vocab_split
fit_21_mon_vocab_balanced <- model_fits_relaxed$fit_21_mon_vocab_balanced

@@

#### Frequency

```{r fixef_21_mon_frequency_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_frequency, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_frequency, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

```{r gaze_time_21_mon_frequency_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_relaxed %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count()

augment(fit_21_mon_frequency) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	# stat_summary(aes(x = ot1, y = .fitted_prob,
	# 				 group = interaction(participant, trial_type),
	# 				 colour = trial_type, fill = trial_type),
	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_frequency) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, frequency_target_childes_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### 2021-10-21 Rmd/report_06_21-mon_stringent.Rmd

```{r define_model_21_mon, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_21_mon <- model_fits$fit_21_mon
fit_21_mon_location <- model_fits$fit_21_mon_location
fit_21_mon_vocab_split<- model_fits$fit_21_mon_vocab_split
fit_21_mon_vocab_balanced <- model_fits$fit_21_mon_vocab_balanced
```

@@

>>>>

```{r define_model_21_mon, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit_21_mon <- model_fits$fit_21_mon
fit_21_mon_location <- model_fits$fit_21_mon_location
fit_21_mon_frequency <- model_fits$fit_21_mon_frequency
fit_21_mon_vocab_split<- model_fits$fit_21_mon_vocab_split
fit_21_mon_vocab_balanced <- model_fits$fit_21_mon_vocab_balanced
```

@@

#### Frequency

```{r fixef_21_mon_frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon_frequency, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon_frequency, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

```{r gaze_time_21_mon_frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants_stringent %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count()

augment(fit_21_mon_frequency) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	# stat_summary(aes(x = ot1, y = .fitted_prob,
	# 				 group = interaction(participant, trial_type),
	# 				 colour = trial_type, fill = trial_type),
	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon_frequency) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, frequency_target_childes_cat, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~frequency_target_childes_cat, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.5, 0.5)) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

### 2021-10-21 Rmd/report_07_2125-mon_relaxed.Rmd

augment(fit_2125_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_wrap(~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0.25, 0.75), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_2125_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, age_group, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0.25, 0.75), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```

>>>>

augment(fit_2125_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot(shape = trial_type, linetype = trial_type) +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	# stat_summary(aes(x = ot1, y = .fitted_prob,
	# 				 group = interaction(participant, trial_type),
	# 				 colour = trial_type, fill = trial_type),
	# 			 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Prime type", fill = "Prime type",
		 shape = "Prime type", linetype = "Prime type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_2125_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, age_group, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	facet_wrap(~age_group, ncol = 1) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Prime type") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "(A) Marginal means of the Growth Curve analysis model (100 ms time bins), plotted in separate\npanels for 21- and 25-month olds. Sample sizes are indicated at the upper left corner in each panel.\n(B) Mean observed probability of target looking, aggregated across time bins.",
		tag_levels = "A"
	) &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	)
```
